---
format: html
engine: knitr
---

## Connect API calls

```{r}
library(httr)
library(dplyr)
library(tidyr)

apiKey <- Sys.getenv("CONNECT_API_KEY")

result <- GET("https://colorado.rstudio.com/rsc/__api__/v1/content",
    add_headers(Authorization = paste("Key", apiKey)))

raw_json <- result |> 
  content()
```

Get all content items (~5200!)

```{r}
raw_df <- raw_json |>
  tibble(data = _) |> 
  unnest_wider(data)

raw_df
```

## Bike Share content

Can get the specific tag id for bike share and then filter using that.

```{r}
bike_tag <- GET("https://colorado.rstudio.com/rsc/__api__/v1/content/3124a8f9-7d30-44b9-a49a-552db71b036e/tags",
    add_headers(Authorization = paste("Key", apiKey)))

raw_json <- result |> 
  content()

bike_tag |> content()
```

Grab a sub-selection of the available columns.

```{r}
bike_content <- GET("https://colorado.rstudio.com/rsc/__api__/v1/tags/217/content",
    add_headers(Authorization = paste("Key", apiKey)))

bike_json <- content(bike_content) |> 
  tibble(data = _) |> 
  unnest_wider(data)

bike_df <- bike_json |> 
  select(guid, name, title, description, content_url, id, content_category, 
         owner_guid, last_deployed_time)
```

This will take the above dataset and write a valid YAML file for use as a listings subsection. 

```{r}
bikeshare_df <- bike_df |> 
  filter(guid %in% c("07b3ff23-595b-4f8b-9f28-7c393cf230ef", "35a5a9c3-f8b1-414a-91cb-bdb5ad402580")) |> 
  select(title = name, url = content_url, date = last_deployed_time) |> 
  mutate(title = glue::glue('<a href="{url}">{title}</a>'),
         title = as.character(title),
         image = "vetiver-bike.png",
         author = "sam.edwardes",
         date = substr(date, 1,10)) |> 
  select(title, date, image, subtitle = author)

# prove that it works
bikeshare_df |> 
  rowwise() |> 
  group_split() |> 
  yaml::as.yaml() |> 
  cat()
```

We can then write it out to a file. Still some potential room for improvement, while the YAML is valid, ideally we would have single quotes around the title element so that it "looks" right when viewed.

```{r}
bikeshare_df |> 
  rowwise() |> 
  group_split() |> 
  write_yaml("test.yml")
```

```{r}
readLines("test.yml") |> 
  paste0(collapse = "\n") |>  
  cat()
```

```{r}
yaml::read_yaml("test.yml") |> 
  tibble(data = _) |> 
  unnest_wider(data)
```

```{r}
yaml::read_yaml("pins.yml") |> 
  tibble(data = _) |> 
  unnest_wider(data)
```



```{r}
bikeshare_df <- data.frame(
  stringsAsFactors = FALSE,
             title = c("<a href=\"https://colorado.rstudio.com/rsc/content/35a5a9c3-f8b1-414a-91cb-bdb5ad402580/\">Bike-Predict---Model-Step-2---Metrics-1654034593681</a>",
                       "<a href=\"https://colorado.rstudio.com/rsc/content/07b3ff23-595b-4f8b-9f28-7c393cf230ef/\">Bike-Predict---Model-Step-1---Train-and-Deploy-1654034008521</a>"),
              date = c("2022-05-31", "2022-05-31"),
             image = c("vetiver-bike.png", "vetiver-bike.png"),
          subtitle = c("sam.edwardes", "sam.edwardes")
)
```

